\documentclass[12pt, a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage[a4paper, portrait, margin=1in]{geometry}
\usepackage{listings}
\usepackage{color}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\footnotesize,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=2
}

\lstset{style=mystyle}


\title{Network application to acquire data from multiple GCO connections and
	   transmit combined data as a single GCO link to TDACS}
\author{Sai Charla}
\date{\today}


\begin{document}
\maketitle
\tableofcontents

\chapter*{Abstract}
\par This project is for developing an application to handle multiple satellite
Thermovac tests at once using a single TDACS system. No changes(Hardware and
software) in the existing system will be necessary. The application will be
loaded into a PC connected to both TDACS and Checkout networks.

\chapter{Introduction}
	\begin{itemize}
			\item Acquire GCO Data from multiple IP addresses(Multiple Satellites
					-Multiple Checkout teams).
			\item Processes the acquired data in to a single stream with the same
					protocols as received data.
			\item Send the data stream to TDACS system.
			\item This ensures the that no hardware or software changes are required
					for present system for acquiring multiple satellite data other than an
					additional PC which acquires data and relays the processed data as if it
					is received from one one GCO.
			\item An Application which can simulate all the above phenomenon for
					testing.
	\end{itemize}

\chapter{Application architecture}
The System acts as server to the present TDACS(which treats it as GCO itself)
and as an independent client to each and every GCO system (Satellite GCO).

\chapter{Source Code Documentation}
\chapter{Future Scope}

\chapter*{References}
	\begin{itemize}
			\item Learning Python Network Programming- Dr.M.O. Faruque Sarkar, Sam
					Washington.
			\item The Definitive Guide to Linux Network Programming- Keir Davis, John
					W.Turner and Nathan Yocom.
			\item Internetworking With TCP/IP vol-III, Client-Server Programming and
					Applications (BSD Socket Version)-David L. Stevens, Douglas E. comer
			\item www.python.org
	\end{itemize}

\chapter*{Appendix A \\Instructions for running the program}

\chapter*{Appendix B \\Ground Checkout communication protocol}
\input{GC_protocol}
\end{document}
